New blog under construction

### 2022-01-29 _posts/welcome/welcome.Rmd
build
Add preview image to welcome post

---
title: "New blog under construction"
description: |
  We're re-launching slinberg.net using Distill. Stand by!
author:
  - name: Steve Linberg
    url: https://slinberg.net
    # affiliation: Spacely Sprockets
    # affiliation_url: https://example.com/spacelysprokets
date: 01-27-2022
output:
  distill::distill_article:
    self_contained: false
---

@@

Pardon the dust while we redecorate. First up will be a soup-to-nuts, zero-to-hero walkthrough of how this site was built and deployed.

>>>>

---
title: "New blog under construction"
description: |
  We're re-launching slinberg.net using Distill. Stand by!
author:
  - name: Steve Linberg
    url: https://slinberg.net
    # affiliation: Spacely Sprockets
    # affiliation_url: https://example.com/spacelysprokets
date: 01-27-2022
output:
  distill::distill_article:
    self_contained: false
preview: construction.png
---

@@

Pardon the dust while we redecorate. First up will be a soup-to-nuts, zero-to-hero walkthrough of how this site was built and deployed on a custom domain with GitHub.
